\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions

### 2014-04-11 lpaper/lunarcont.tex
Added Diego Fixes

\begin{abstract}
It is often the case that games have continuous dynamics and allow for continuous actions, possibly with with some added noise. For larger games with complicated dynamics, having agents learn offline behaviours in such a setting is a daunting task. On the other hand, provided a forward model is available, one might try to spread the cost of search/learning in a rolling horizon fashion (e.g. as in Monte Carlo Tree Search). In this paper we compare T-HOLOP (Truncated Hierarchical Open Loop Planning), an open loop planning algorithm at least partially inspired by MCTS, with a version of evolutionary planning that uses CMA-ES (which we call EVO-P) in two planning benchmark problems (Cart Balancing and the Double Integrator) and in Lunar Lander, a classic arcade game. We show that EVO-P outperforms T-HOLOP in the classic benchmarks, while T-HOLOP is unable to find a solution using the same heuristics. We conclude that off-the-shelf evolutionary algorithms can be used successfully in a rolling horizon setting, and that a different type of heuristics might be needed under different optimisation algorithms.

@@

Once a satisfactory plan/policy has been estimated (or the agent runs out of time, iterations etc. ) it proceeds by executing the first action of the plan, thus moving to the next state. Once there, the agent performs the same sequence of ``mental'' actions, (i.e. plans and executes the first action), until some predefined stopping condition.  In this paper we will concern ourselves \textit{only} with this method of planning. What changes from method to method is how the plan is formed. The main version of the algorithm used can be seen in Algorithm \ref{algo:ooop}.

@@

\section{Methodology} \label{sec:methodology}
Our methodology is simple, yet efficient. We test T-HOLOP and EVO-P in two simple benchmark problems (see below for more detail) and n Lunar Lander, a classic arcade game. EVO-P is simply CMA-ES used in a rolling horizon setting, while T-HOLOP is T-HOO used in the same manner.

@@

         \caption{Performance of both T-HOLOP and EVO-P in the Inverted Pendulum benchmark (error bars for the 95th percentile). Higher scores are better}
         \label{fig:IP-all}

@@

       \caption{Performance of all algorithms in the Double Integrator benchmark (error bars for the 95th percentile). Higher scores are better}

@@

  \centering
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map2.pdf}
                \caption{Map A,  where the ship is lower then the pad}
                \label{fig:map2}
        \end{subfigure}  
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-easy.pdf}
                \caption{Map B, an easy map where only the first heuristic is used}
                \label{fig:map1-easy}

        \end{subfigure}
\\
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-tall.pdf}
                \caption{Map C, where the ship is close to the top of the screen}
                \label{fig:map1-tall}\end{subfigure}\begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-wall.pdf}
                \caption{Map D, where the ship is behind a wall }
                \label{fig:map-wall}

@@

         \caption{The four different maps used in our experiments. The maps capture different position/properties}
         \label{fig:maps}

@@

\begin{table}[h]
	\begin{tabular}{lrrrr}
\hline
 Map Name   &   Success Mean &   Success CI &   Ticks Mean &   Tick CI \\
\hline
 Map A       &            1   &     0        &       2925.9 &   $\pm 184.437$ \\
 Map B  &            1   &     0        &       2733   &   $\pm 159.34$  \\
 Map C  &            1   &     0        &       2293   &   $\pm 123.917$ \\
 Map D  &            0.9 &     $\pm 0.226216$ &       2421.6 &   $\pm 682.893$ \\
\hline
\end{tabular}
\label{tb:results}
\caption{EVO-P results for different Lunar Lander maps}
\end{table}

@@

% Use \section* for the acknowledgments
\section*{Acknowledgements}
This work was supported by EPSRC grant EP/H048588/1 entitled:``UCT for Games and Beyond'' and an EPSRC Ph.D studentship.

>>>>

\begin{abstract}
It is often the case that games have continuous dynamics and allow for continuous actions, possibly with with some added noise. For larger games with complicated dynamics, having agents learn offline behaviours in such a setting is a daunting task. On the other hand, provided a generative model is available, one might try to spread the cost of search/learning in a rolling horizon fashion (e.g. as in Monte Carlo Tree Search). In this paper we compare T-HOLOP (Truncated Hierarchical Open Loop Planning), an open loop planning algorithm at least partially inspired by MCTS, with a version of evolutionary planning that uses CMA-ES (which we call EVO-P) in two planning benchmark problems (Inverted Pendulum and the Double Integrator) and in Lunar Lander, a classic arcade game. We show that EVO-P outperforms T-HOLOP in the classic benchmarks, while T-HOLOP is unable to find a solution using the same heuristics. We conclude that off-the-shelf evolutionary algorithms can be used successfully in a rolling horizon setting, and that a different type of heuristics might be needed under different optimisation algorithms.

@@

Once a satisfactory plan/policy has been estimated (or the agent runs out of time, iterations etc.) it proceeds by executing the first action of the plan, thus moving to the next state. Once there, the agent performs the same sequence of ``mental'' actions, (i.e. plans and executes the first action), until some predefined stopping condition.  In this paper we will concern ourselves \textit{only} with this method of planning. What changes from method to method is how the plan is formed. The main version of the algorithm used can be seen in Algorithm \ref{algo:ooop}.

@@

\section{Methodology} \label{sec:methodology}
Our methodology is simple, yet efficient. We test T-HOLOP and EVO-P in two simple benchmark problems (see below for more detail) and in Lunar Lander, a classic arcade game. EVO-P is simply CMA-ES used in a rolling horizon setting, while T-HOLOP is T-HOO used in the same manner.

@@

         \caption{Performance of both T-HOLOP and EVO-P in the Inverted Pendulum benchmark (error bars for the 95th percentile). Higher scores are better.}
         \label{fig:IP-all}

@@

       \caption{Performance of all algorithms in the Double Integrator benchmark (error bars for the 95th percentile). Higher scores are better.}

@@

  \centering
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map2.pdf}
                \caption{Map A,  where the ship is lower then the pad.}
                \label{fig:map2}
        \end{subfigure}  
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-easy.pdf}
                \caption{Map B, an easy map where only the first heuristic is used.}
                \label{fig:map1-easy}

        \end{subfigure}
\\
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-tall.pdf}
                \caption{Map C, where the ship is close to the top of the screen.}
                \label{fig:map1-tall}\end{subfigure}\begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-wall.pdf}
                \caption{Map D, where the ship is behind a wall.}
                \label{fig:map-wall}

@@

         \caption{The four different maps used in our experiments. The maps capture different position/properties.}
         \label{fig:maps}

@@

\begin{table}[h]
	\begin{tabular}{lrrrr}
\hline
 Map Name   &   Success Mean &   Success CI &   Ticks Mean &   Tick CI \\
\hline
 Map A       &            1   &     0        &       2925.9 &   $\pm 184.437$ \\
 Map B  &            1   &     0        &       2733   &   $\pm 159.34$  \\
 Map C  &            1   &     0        &       2293   &   $\pm 123.917$ \\
 Map D  &            0.9 &     $\pm 0.226216$ &       2421.6 &   $\pm 682.893$ \\
\hline
\end{tabular}
\label{tb:results}
\caption{EVO-P results for different Lunar Lander maps.}
\end{table}

@@

% Use \section* for the acknowledgments
\section*{Acknowledgements}
This work was supported by EPSRC grant EP/H048588/1 entitled: ``UCT for Games and Beyond'' and an EPSRC Ph.D studentship.
